\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,margin=0.65in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

\definecolor{heading}{HTML}{172033}
\definecolor{accent}{HTML}{0F766E}
\definecolor{textgray}{HTML}{374151}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=2pt}
\titleformat{\section}{\large\bfseries\color{heading}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{9pt}{5pt}

\begin{document}

{\Huge \textbf{Ashish Prajapati}}\\
{\large Business Analyst \& IT Project Lead}\\
Bengaluru, India \\
\href{mailto:prajapati.ashish2108@gmail.com}{prajapati.ashish2108@gmail.com}
\textbar\ +91 80730 17966
\textbar\ \href{https://linkedin.com/in/ashishprajapati21}{linkedin.com/in/ashishprajapati21}
\textbar\ \href{https://itsmeashish2108.github.io/ashish-portfolio-site/}{Portfolio}

\section*{Professional Summary}
Business Analyst and IT Project Lead specializing in ERP systems, workflow automation, integrations, SQL validation, API testing, UAT, documentation, and operational systems. I convert ambiguous business problems into structured requirements, process maps, system rules, validation scenarios, rollout documentation, and adoption-ready workflows.

\section*{Core Skills}
\textbf{Business Analysis:} BRD, FRD, stakeholder discovery, requirement gathering, gap analysis, user stories, acceptance criteria, business rules.\\
\textbf{Process \& Operations:} Process mapping, SOPs, workflow design, root cause analysis, rollout planning, change management.\\
\textbf{ERP \& Systems:} ERPNext, Frappe, operational workflows, role permissions, approval flows, master data.\\
\textbf{Data \& Validation:} SQL, Excel, data validation, reconciliation, field mapping, reports, dashboards.\\
\textbf{API \& Integrations:} Postman, REST APIs, Shopify, Shiprocket, payment workflows, GST e-invoicing.\\
\textbf{Testing \& Delivery:} UAT, test cases, defect tracking, production support, issue triage, sign-off documentation.

\section*{Selected Project Experience}
\textbf{ERP Workflow Automation}
\begin{itemize}
  \item Documented current-state operations and designed future-state ERP workflows across operations, inventory, quality, and finance processes.
  \item Defined fields, validations, role permissions, approval flows, UAT scenarios, and rollout documentation.
  \item Improved process visibility, reduced manual Excel dependency, and supported ERP adoption.
\end{itemize}

\textbf{Shopify to ERP Integration}
\begin{itemize}
  \item Created field mappings, sync rules, validation scenarios, exception handling notes, and UAT test cases.
  \item Supported reliable order and inventory data flow between Shopify and ERP systems.
  \item Improved order flow visibility and reduced reconciliation effort.
\end{itemize}

\textbf{Shiprocket / Logistics Workflow Integration}
\begin{itemize}
  \item Mapped shipment lifecycle stages, status transitions, operational handoffs, and failure cases.
  \item Tested API responses and documented scenarios for logistics workflow alignment.
  \item Improved shipment tracking clarity and cross-functional coordination.
\end{itemize}

\textbf{GST E-invoicing / Finance Workflow Support}
\begin{itemize}
  \item Captured finance requirements, defined business rules, and documented exception scenarios.
  \item Supported UAT, SQL validation, and compliance-oriented workflow documentation.
  \item Improved invoice workflow readiness and finance process reliability.
\end{itemize}

\textbf{Quality / Inventory Process Improvements}
\begin{itemize}
  \item Mapped shop-floor, warehouse, production, quality, and inventory workflows.
  \item Identified bottlenecks, manual tracking gaps, deviations, and traceability issues.
  \item Translated operational observations into ERP-based workflow improvement opportunities.
\end{itemize}

\section*{Experience}
\textbf{Business Analyst \& IT Project Lead}\\
Own business analysis and system delivery responsibilities for ERP and integration workstreams, including discovery, requirement documentation, workflow design, UAT, rollout support, and production issue resolution. Coordinate with a 6-member IT development team and multiple business teams to deliver operational systems.

\textbf{Process Engineer Intern to Full-time}\\
Mapped shop-floor, warehouse, production, quality, and inventory workflows to identify bottlenecks, manual tracking gaps, repacking leakages, deviations, and Excel-dependent processes. Translated operational observations into structured improvement opportunities.

\section*{Education \& Certification}
\textbf{BE, Sri Venkateswara College of Engineering} -- CGPA 7.77\\
\textbf{Business Analysis \& Process Management} -- Coursera, 2025

\end{document}
